Co-moving stars in \textsl{Gaia DR1}

### 2016-11-10 paper/ms.tex
Modify raverv and hist_sep figures and captions

We construct the initial sample of pairs as follows.
We first apply a global parallax S/N cut of 8 to \tgas, which leaves 619,618 stars.
Then, for each star, we search a potential co-moving partner star with a
difference in tangential velocity $\absdvtan < 10$~\kms\ within 10 pc
using RA, DEC, a point-estimate of the distance, and the proper motions.
Throughout this \documentname\, we use the following estimator for
the point-estimate of the distance applying a correction for the Lutz-Kelker bias
(\citealt{Lutz:1973aa}):
\begin{equation}
  d = 1000 \, \left[\frac{\varpi}{2} \,
    \left(1 + \sqrt{1 - \frac{16}{\snr^2}} \right) \right]^{-1} \, {\rm pc}
\end{equation}
where $\varpi$ is the parallax in mas.
The difference in tangential velocity between two stars is, then,
\begin{equation}
  \absdvtan = |d_1 \vec\mu_1 - d_2 \vec\mu_2|
\end{equation}
where $\vec\mu = (\mu_\alpha, \mu_\delta)$.

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/glon_d_pie.pdf}
  \end{center}
  \caption{%
    Panoramic view of co-moving pairs of stars. The angle is the Galactic
    longitude, and the distance is in pc.
    Pair networks of sizes less than 5 are connected by gray lines.
    Pair networks of size $\geq 5$ are plotted with a unique color per network.
    We also show the positions of known Milky Way star clusters
    from \citet{Kharchenko:2016aa} as empty purple circles,
    and stars in OB associations from \citet{de-Zeeuw:1999aa} as
    black circles.
    \label{fig:glon_d_pairlines}}
\end{figure*}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/raverv.pdf}
  \end{center}
  \caption{%
    Radial velocity differences of 283 pairs with \rave\ measurements.
    Left: $\Delta v_r$ in units of $\sigma_{\Delta v_r} = \sqrt{\sigma_{v_r,1}^2 + \sigma_{v_r,2}^2}$
    as a function of physical separation.
    We highlight $3\sigma$ limit in gray shades.
    Right: Fraction of pairs with $\Delta v_r/\sigma_{\Delta v_r} <3$
    as a function of physical separation. We calculate the fraction with a running
    bin containing 31 data points at a time.
    The median, and the minimum and maximum separation of pairs in each bin are
    indicated with a marker, and its errorbars.
    We separate pairs with network size of 2 (i.e., mutually exclusively connected)
    from those in larger networks.
    \label{fig:raverv}}
\end{figure*}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/hist_sep.pdf}
  \end{center}
  \caption{%
    Separation distribution of co-moving pairs of stars. 
    We divide the pairs into those mutually exclusively connected
    (network size $=2$), and those connected to larger networks (size $>2$).
    \label{fig:hist_separation}
    }
\end{figure*}

>>>>

We construct the initial sample of pairs as follows.
We first apply a global parallax S/N cut of 8 to \tgas, which leaves 619,618 stars.
Then, for each star, we search a potential co-moving partner star with a
difference in tangential velocity $\absdvtan < 10$~\kms\ within 10 pc
using RA, DEC, a point-estimate of the distance, and the proper motions.
Throughout this \documentname\, we use the following estimator for
the point-estimate of the distance applying a correction for the Lutz-Kelker bias
(\citealt{Lutz:1973aa}):
\begin{equation}
  d = 1000 \, \left[\frac{\varpi}{2} \,
    \left(1 + \sqrt{1 - \frac{16}{\snr^2}} \right) \right]^{-1} \, {\rm pc}
    \label{eq:dist}
\end{equation}
where $\varpi$ is the parallax in mas.
The difference in tangential velocity between two stars is, then,
\begin{equation}
  \absdvtan = |d_1 \vec\mu_1 - d_2 \vec\mu_2|
\end{equation}
where $\vec\mu = (\mu_\alpha, \mu_\delta)$.

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/glon_d_pie.pdf}
  \end{center}
  \caption{%
    Panoramic view of co-moving pairs of stars. This is a cylindrical
    projection of onto the Galactic plane. The angle is the Galactic
    longitude, and the radius is $d\cos b$ in pc where $d$ is the point-estimate
    of distance using Equation~\ref{eq:dist}.
    Pairs in connected components of sizes less than 5 are connected by gray lines.
    Pair in connected components of size $\geq 5$ are plotted with a unique color per network,
    and their nodes (stars) are highlighted with small black circles.
    We also show the positions of known Milky Way star clusters
    from \citet{Kharchenko:2016aa} as empty purple circles,
    and stars in OB associations from \citet{de-Zeeuw:1999aa} as
    gray circles.
    \label{fig:glon_d_pairlines}}
\end{figure*}

@@

\begin{figure}[htbp]
  \begin{center}
    % \includegraphics[width=\linewidth]{figures/raverv.pdf}
    \includegraphics[width=.5\linewidth]{figures/raverv.pdf}
  \end{center}
  \caption{%
    Validation of candidate co-moving pairs using radial velocities from \rave.
    Top: Radial velocity differences, $\Delta v_r$, of 283 pairs with \rave\ measurements.
    $\Delta v_r$ is plotted in units of $\sigma_{\Delta v_r} = \sqrt{\sigma_{v_r,1}^2 + \sigma_{v_r,2}^2}$
    as a function of physical separation.
    We highlight $3\sigma$ limit with two horizontal lines.
    Bottom: Fraction of pairs with $\Delta v_r/\sigma_{\Delta v_r} <3$
    as a function of physical separation. We calculate the fraction with a running
    bin containing 31 data points at a time.
    The median, and the minimum and maximum separation of pairs in each bin are
    indicated with a marker, and its errorbars.
    We separate pairs in connected components of size 2 (i.e., mutually exclusively connected)
    from those in larger connected components.
    \label{fig:raverv}}
\end{figure}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/hist_sep.pdf}
  \end{center}
  \caption{%
    Separation distribution of co-moving pairs of stars.
    As with Figure~\ref{fig:raverv},
    we divide the pairs into those mutually exclusively connected
    (connected component size $=2$), and those connected to larger connected components (size $>2$).
    \label{fig:hist_separation}
    }
\end{figure*}
